\documentclass{article}
\usepackage{graphicx}
\usepackage[cm]{fullpage}
\usepackage{url}

\renewcommand{\arraystretch}{1.5}

\begin{document}


\title{\textsc{Cryptotronix Contributor Agreement}}
\date{}
\maketitle

This Cryptotronix Contributor Agreement (``CCA'') applies to any
contribution that you make to any product or project managed by us
(the ``project''), and sets out the intellectual property rights you
grant to us in the contributed materials. The term ``us'' shall mean
Cryptotronix, LLC. The term ``you'' shall mean the person
or entity identified below. If you agree to be bound by these terms,
fill in the information requested below and sign the CCA where
indicated below. Read this agreement carefully before signing. These
terms and conditions constitute a binding legal agreement.

\begin{enumerate}
\item The term ``contribution'' or ``contributed materials'' means any
  source code, object code, patch, tool, sample, graphic,
  specification, manual, documentation, or any other material posted
  or submitted by you to the project.

\item With respect to any worldwide copyrights, or copyright
  applications and registrations, in your contribution:

\begin{itemize}
\item you hereby assign to us joint ownership, and to the extent that
  such assignment is or becomes invalid, ineffective or unenforceable,
  you hereby grant to us a perpetual, irrevocable, non-exclusive,
  worldwide, no-charge, royalty-free, unrestricted license to exercise
  all rights under those copyrights. This includes, at our option, the
  right to sublicense these same rights to third parties through
  multiple levels of sublicensees or other licensing arrangements;
\item you agree that each of us can do all things in relation to your
  contribution as if each of us were the sole owners, and if one of us
  makes a derivative work of your contribution, the one who makes the
  derivative work (or has it made) will be the sole owner of that
  derivative work;
\item you agree that you will not assert any moral rights in your
  contribution against us, our licensees or transferees;
\item you agree that we may register a copyright in your contribution
  and exercise all ownership rights associated with it; and
\item you agree that neither of us has any duty to consult with,
  obtain the consent of, pay or render an accounting to the other for
  any use or distribution of your contribution.
\end{itemize}

\item With respect to any patents you own, or that you can license
  without payment to any third party, you hereby grant to us a
  perpetual, irrevocable, non-exclusive, worldwide, no-charge,
  royalty-free license to:
\begin{itemize}
\item make, have made, use, sell, offer to sell, import, and otherwise
  transfer your contribution in whole or in part, alone or in
  combination with or included in any product, work or materials
  arising out of the project to which your contribution was submitted,
  and
\item at our option, to sublicense these same rights to third parties
  through multiple levels of sublicensees or other licensing
  arrangements.
\end{itemize}

\item Except as set out above, you keep all right, title, and interest
  in your contribution. The rights that you grant to us under these
  terms are effective on the date you first submitted a contribution
  to us, even if your submission took place before the date you sign
  these terms. Any contribution we make available under any license
  will also be made available under a suitable FSF (Free Software
  Foundation) or OSI (Open Source Initiative) approved license.

\item You covenant, represent, warrant and agree that:
\begin{itemize}
\item each contribution that you submit is and shall be an original
  work of authorship and you can legally grant the rights set out in
  this CCA;
\item to the best of your knowledge, each contribution will not
  violate any third party's copyrights, trademarks, patents, or other
  intellectual property rights; and
\item each contribution shall be in compliance with U.S. export
  control laws and other applicable export and import laws.
\end{itemize}

You agree to notify us if you become aware of any circumstance which
would make any of the foregoing representations inaccurate in any
respect. Cryptotronix may publicly disclose your participation in the
project, including the fact that you have signed the CCA.

\item This CCA is governed by the laws of the State of Colorado and
  applicable U.S. Federal law. Any choice of law rules will not apply.

\item Please place an “x” on one of the applicable statement below.
  Please do NOT mark both statements:

\begin{itemize}
  \item[] \underline{\hspace{1cm}} I am signing on behalf of myself
  as an individual and no other person or entity, including my
  employer, has or will have rights with respect my contributions.
\item[] \underline{\hspace{1cm}} I am signing on behalf of my employer
  or a legal entity and I have the actual authority to contractually
  bind that entity.
\end{itemize}
\end{enumerate}


\begin{center}
  \begin{tabular}{ | l | p{12cm} | }
    \hline
    Name* &  \\ \hline
    Company's Name (if applicable) &  \\ \hline
    Mailing Address* &  \\ \hline
    Mailing Address (cont'd) &  \\ \hline
    Telephone, Fax, and Email* &  \\ \hline
    Signature* &  \\ \hline
    Date* &  \\ \hline
    Project Name* &  \\ \hline
    Username (if applicable) &  \\ \hline
    \end{tabular}
  \end{center}

  {\footnotesize * Required field}

  \bigskip\hrule\bigskip

  {\footnotesize Cryptotronix Contributor Agreement version
  1.0, a modiﬁed version of Oracle Contributor Agreement version
  1.7.1,

  This document is licensed under a Creative Commons Attribution-Share
  Alike 3.0 Unported License

  \url{http://creativecommons.org/licenses/by-sa/3.0/}}

\end{document}